An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-28 VLDB2026/main.tex

	\textit{\textbf{Index size.}}
	\sout{Traditional graph-based methods often only evaluate the size of the generated graph index and do not include the original data, while the index generated by the IVF-based method includes the original data. }
	In order to unify the comparison standard, we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
	% Traditional graph-based methods often evaluate only the size of the generated index, excluding the original data, whereas IVF-based methods include it. To ensure a consistent comparison, we consider both the index structure and the original data when measuring index size.
	As shown in the Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets. This overhead stems primarily from its extensive metadata requirements. The index sizes of other methods show moderate variation. Among these, Faiss generates slightly smaller indexes due to its efficient index design.

>>>>

	\textit{\textbf{Index size.}}
%	Traditional graph-based methods often only evaluate the size of the generated graph index and do not include the original data, while the index generated by the IVF-based method includes the original data. In order to unify the comparison standard, 
%	we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
To ensure a fair comparison with IVF-based algorithms, we include the original dataset in the index size calculation for graph-based indexes.
	% Traditional graph-based methods often evaluate only the size of the generated index, excluding the original data, whereas IVF-based methods include it. To ensure a consistent comparison, we consider both the index structure and the original data when measuring index size.
	As shown in the Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets. This overhead stems primarily from its extensive metadata requirements. The index sizes of other methods show moderate variation. Among these, Faiss generates slightly smaller indexes due to its efficient index design.
